# First look at KCMO 311 data
efg, UMKC Center for Health Insights.  
2013-12-12.  Last modified 2014-10-08.  

## Frequency Counts of Kansas City, MO 311 Reports
https://data.kcmo.org/311/KCMOPS311-Data/7at3-sxhp  
2014-10-08  

```{r, echo=FALSE}
setwd("C:/Data/Cities/KCMO/data-kcmo-org/KCMOPS311/")
filename <-  "KCMOPS311-2014-10-08-121800.csv"
d <- read.csv(filename, as.is=TRUE, colClasses="character")

# See if any type conversion problems exist
d$CreationDate  <- as.POSIXct( strptime(d$CREATION.DATE, "%m/%d/%Y") )
d$CreationMonth <- as.integer(d$CREATION.MONTH)
d$CreationYear  <- as.integer(d$CREATION.YEAR)

d$CloseDate  <- as.POSIXct( strptime(d$CLOSED.DATE, "%m/%d/%Y") )
d$CloseMonth <- as.integer(d$CLOSED.MONTH)
d$CloseYear  <- as.integer(d$CLOSED.YEAR)

d$DaysToClose <- as.integer(d$DAYS.TO.CLOSE)

d$XCoordinate <- as.numeric(d$XCOORDINATE)
d$YCoordinate <- as.numeric(d$YCOORDINATE)
options(width=120)
```
The current file has `r nrow(d)` rows by `r ncol(d)` columns.

There are `r length(unique(d$CASE.ID))` unique CASE.IDs.

## Source
Reports by Source:
```{r}
table(d$SOURCE)
```

Reports by Source and Creation Year:
```{r}
table(d$SOURCE, d$CreationYear)
```

## Department
Reports by City Department:
```{r}
table(d$DEPARTMENT)
```

Reports by City Department by Creation Year:
```{r}
table(d$DEPARTMENT, d$CreationYear)
```

## Creation Year
Reports by Creation Year and Month:
```{r}
table(d$CreationYear)
table(d$CreationMonth)
table(d$CreationYear, d$CreationMonth)
```

## Status
Reports by Status:
```{r}
table(d$STATUS)
```

Reports by Status and Creation Year:
```{r}
table(d$STATUS, d$CreationYear)
```
## Exceeded Estimate Timeframe
```{r}
table(d$EXCEEDED.EST.TIMEFRAME)
table(d$EXCEEDED.EST.TIMEFRAME, d$CreationYear)
```

## Creation Year vs Close Year
Reports by Creation Year and Close Year
```{r}
table(d$CreationYear, d$CloseYear)
```

Histogram of Days To Close:
```{r}
options(scipen=999) # suppress scientific notation
hist(d$DaysToClose, main="Days to Close")
```

Since the histogram is skewed, introduce a log10 transformation:
```{r}
hist(log10(1+d$DaysToClose))
```

## ZIP Code
```{r}
table(d$ZIP.CODE)
table(d$ZIP.CODE, d$CreationYear)
```

## City Council District
```{r}
table(d$COUNCIL.DISTRICT)
table(d$COUNCIL.DISTRICT, d$CreationYear)
```

## Quality of Service
```{r}
table(d$QUALITY.OF.SERVICE)
table(d$QUALITY.OF.SERVICE, d$CreationYear)
```

## Timeliness of Service
```{r}
table(d$TIMELINESS.OF..SERVICE)
table(d$TIMELINESS.OF..SERVICE, d$CreationYear)
```

## Customer Service
```{r}
table(d$CUSTOMER.SERVICE)
table(d$CUSTOMER.SERVICE, d$CreationYear)
```                                                                      

## Other Data

Lists from remaining data fields are farily long, so they will be shown separately.
```{r}
length(table(d$WORK.GROUP))
length(table(d$REQUEST.TYPE))  
length(table(d$NEIGHBORHOOD))             
```

* STREET.ADDRESS
* ADDRESS.WITH.GEOCODE
* PARCEL.ID.NO
* XCOORDINATE
* YCOORDINATE

## Structure of data.fame

Includes extra variables from conversions.
```{r}
str(d)
```