# KCMO 311 data:  Health Department
efg, UMKC Center for Health Insights.  
2013-12-12.  Last modified 2014-10-08.  

## Frequency Counts of Kansas City, MO 311 Reports
https://data.kcmo.org/311/KCMOPS311-Data/7at3-sxhp  
2014-10-08  

```{r, echo=FALSE}
setwd("C:/Data/Cities/KCMO/data-kcmo-org/KCMOPS311/")
filename <-  "KCMOPS311-2014-10-08-121800.csv"
d <- read.csv(filename, as.is=TRUE, colClasses="character")
# See if any type conversion problems exist
d$CreationDate  <- as.Date(d$CREATION.DATE, "%m/%d/%Y") 
d$CreationMonth <- as.integer(d$CREATION.MONTH)
d$CreationYear  <- as.integer(d$CREATION.YEAR)

d$CloseDate  <- as.Date(d$CLOSED.DATE, "%m/%d/%Y") 
d$CloseMonth <- as.integer(d$CLOSED.MONTH)
d$CloseYear  <- as.integer(d$CLOSED.YEAR)

d$DaysToClose <- as.integer(d$DAYS.TO.CLOSE)

d$XCoordinate <- as.numeric(d$XCOORDINATE)
d$YCoordinate <- as.numeric(d$YCOORDINATE)
options(width=120)
```
The current file has `r nrow(d)` rows.

## Health Department

```{r}
health <- d[d$DEPARTMENT == "Health", ]
dim(health)  
```

There are `r nrow(health)` Health Department records in the file of `r nrow(d)` records.

### Source by Year
```{r}
table(health$SOURCE, health$CreationYear)
```

### Status
Reports by Status:
```{r}
table(health$STATUS,health$CreationYear)
```                      

### Creation Year
Reports by Creation Year and Month:
```{r}
table(health$CreationYear, health$CreationMonth)
```                                      

### Work Group by Year
```{r}
table(health$WORK.GROUP, health$CreationYear)
```

### Creation Year vs Close Year
Reports by Creation Year and Close Year
```{r}
table(health$CreationYear, health$CloseYear)
```                                                   

### Request Type by Year
```{r}
counts <- as.data.frame.matrix(table(health$REQUEST.TYPE, health$CREATION.YEAR))

counts <- cbind(counts, TOTAL=apply(counts,1,sum))
counts <- rbind(counts, TOTAL=apply(counts,2,sum))

counts                                                                                        
```

### ZIP Code by Year
```{r}
table(health$ZIP.CODE, health$CreationYear)
```

### City Council District by Year
```{r}
table(health$COUNCIL.DISTRICT, health$CreationYear)
```

### Quality of Service by Year
```{r}
table(health$QUALITY.OF.SERVICE, health$CreationYear)
```

### Timeliness of Service by Year
```{r}
table(health$TIMELINESS.OF..SERVICE, health$CreationYear)
```

### Customer Service by Year
```{r}
table(health$CUSTOMER.SERVICE, health$CreationYear)
```               

### Top 50 Addresses
```{r}
counts <- sort(table(health$ADDRESS.WITH.GEOCODE), decreasing=TRUE)
counts <- data.frame(Address=names(counts), Counts=counts)
row.names(counts) <- 1:nrow(counts)
head(counts, 50)
```                     